Computer Science House Constitution

### 2024-10-07 constitution.tex
add explicit mechanisms for housing priority access & automatic NTID access improvement

\asubsection{Housing Priority System}
The Housing Priority System is a means for determining the priority a member has in a housing issue or the assignment of available housing.
The member with top priority is the member with On-Floor Status and the most Housing Priority Points.
Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Eval.
Each Active Member who passes the Membership Eval is granted two Housing Priority Points.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.
The number of Eligible Votes is determined when a vote is called and remains fixed throughout the duration of the vote.

>>>>

\asubsection{Housing Priority System}
The Housing Priority System is a means for determining the priority a member has in a housing issue or the assignment of available housing.
The member with top priority is the member with On-Floor Status and the most Housing Priority Points.
Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Eval.
Each Active Member who passes the Membership Eval is granted two Housing Priority Points.
Members registered with NTID receive priority over members with equivalent Housing Priority points. % NTID students can ONLY choose dorms with doorbells, so this helps ensure that students who need these rooms have access to them. 
Members who require accommodations may be temporarily granted additional Housing Priority Points at the request of RIT Housing or at the discretion of the Evaluations Director. 
Temporary Housing Priority Points remain in effect until the end of the Standard Operating Session or an earlier date, as specified when granted.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.
